Guarded Recursion in Agda via Sized Types

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
more differences with Clouston et al

Utilizing techniques for representing ``type theory in type theory''
\cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
the syntax of a simple type theory for guarded recursion. This object
language, which we call \GTT, is a variant of Atkey and McBride's type
system for productive coprogramming \cite{atkey2013productive} in
which the clock context can contain at most one clock. The types of
\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
a nameless analogue of Atkey and McBride's universal clock
quantification. Clouston \etal \ \cite{CloustonBGB15} studied a
guarded variant of lambda calculus extended with a \IC{□} operation,
which they call ``constant''.  Our object calculus differs from
theirs in that our judgments are indexed by a clock context, which can
be empty or containing exactly one clock. 
%In this respect \GTT\ is closer in spirit to Atkey and McBride's
%language.
The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
\IC{□} than Clouston et al.'s.

>>>>

Utilizing techniques for representing ``type theory in type theory''
\cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
the syntax of a simple type theory for guarded recursion. This object
language, which we call \GTT, is a variant of Atkey and McBride's type
system for productive coprogramming \cite{atkey2013productive} in
which the clock context can contain at most one clock. The types of
\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
a nameless analogue of Atkey and McBride's universal clock
quantification. Clouston \etal \ \cite{CloustonBGB15} studied a
guarded variant of lambda calculus extended with a \IC{□} operation,
which they call ``constant''.  Our object calculus differs from
theirs in that our judgments are indexed by a clock context, which can
be empty or containing exactly one clock. 
%In this respect \GTT\ is closer in spirit to Atkey and McBride's
%language.
The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
\IC{□} than Clouston \etal 's.
\GTT\ also differs from Clouston \etal 's calculus in the class of definable
guarded recursive types. We follow Atkey and McBride's approach and
restrict the least fixpoint operator \IC{μ} to act on strictly positive
functors, while Clouston \etal' \IC{μ} type former operates solely on functors
in which all variables are guarded by an occurrence of the \IC{▻} modality.
